Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
add VODE cite

Prior to \maestroex, we developed the low Mach number code \maestro. Like \maestroex, \maestro~is a block-structured adaptive mesh refinement (AMR) code for modelling low Mach number astrophysical codes. Its development is described in a series of papers: \cite{Almgren2006a,Almgren2006b,Almgren2008a,Zingale2009,Nonaka2010}. In \maestro, the system of low Mach number equations is solved using an explicit Godunov approach for the advection, a stiff ODE solver for the reactions (VODE, CITE), and multigrid linear solvers for the pressure projection steps. Strang splitting CITE is used to integrate the thermodynamic variables, a second order projection method to integrate the velocity subject to the divergence constraint, and a velocity splitting scheme to hydrodynamically evolve the base state. The original \maestro~code was developed using the pure Fortran 90 \fboxlib~software framework \cite{Zhang2016}; \maestroex~instead uses the C++/Fortran 90 \amrex~framework \cite{Zhang2019}.

>>>>

Prior to \maestroex, we developed the low Mach number code \maestro. Like \maestroex, \maestro~is a block-structured adaptive mesh refinement (AMR) code for modelling low Mach number astrophysical codes. Its development is described in a series of papers: \cite{Almgren2006a,Almgren2006b,Almgren2008a,Zingale2009,Nonaka2010}. In \maestro, the system of low Mach number equations is solved using an explicit Godunov approach for the advection, a stiff ODE solver for the reactions (VODE~\cite{vode}), and multigrid linear solvers for the pressure projection steps. Strang splitting CITE is used to integrate the thermodynamic variables, a second order projection method to integrate the velocity subject to the divergence constraint, and a velocity splitting scheme to hydrodynamically evolve the base state. The original \maestro~code was developed using the pure Fortran 90 \fboxlib~software framework \cite{Zhang2016}; \maestroex~instead uses the C++/Fortran 90 \amrex~framework \cite{Zhang2019}.
